Large-strain matrix-free finite element solver of hyperelastic problems with geometric multigrid preconditioner

### 2018-09-03 doc/large_strain.tex
add figures and use in latex
replot Emmy figures (now correct memory) and add IWR to Latex
add abstract and title

@@

@@

>>>>

\usepackage[format=plain,indention=.5cm]{caption}
\usepackage[labelformat=simple]{subcaption}
\renewcommand\thesubfigure{(\alph{subfigure})}

@@

\begin{frontmatter}
  \title{
  Large-strain matrix-free finite element solver of hyperelastic problems with geometric multigrid preconditioner
  }

  \author[a]{Denis Davydov\corref{cor}}
  \ead{denis.davydov@fau.de}

  \author[a]{Jean-Paul Pelteret}
  \ead{jean-paul.pelteret@fau.de}

  \author[b]{Daniel Arndt}
  \ead{daniel.arndt@iwr.uni-heidelberg.de}

  \author[a]{Paul Steinmann}
  \ead{paul.steinmann@fau.de}

  \cortext[cor]{Corresponding author.}

  \address[a]{Chair of Applied Mechanics,
  Friedrich-Alexander-Universit\"{a}t Erlangen-N\"{u}rnberg,
  Egerlandstr.\ 5, 91058 Erlangen, Germany}

  \address[b]{Interdisciplinary Center for Scientific Computing (IWR),
      Heidelberg University,
      Im Neuenheimer Feld 205,
      69120 Heidelberg,
      Germany}

  \begin{abstract}
    Solution of source problems on modern computer architectures is typically memory banded.
    Loading matrix elements is significantly slower than performing the arithmetic operations when solving the problem.
    In order to improve the performance of the iterative solver, the so-called matrix-free methods are
    widely adopted in fluid mechanics community, where the matrix vector products are formed on-the-fly.

    In this work we advance the application of matrix-free approaches to problems in solid mechanics.
    We propose and numerically investigate different implementations of the large-strain hyper-elastic tangent operator.
    In order to improve the convergence of iterative solvers, we also propose a way to construct a level tangent operator
    and employ it to define a geometric multigrid preconditioner.
    Our implementation employs MPI and Intel Threading Building Blocks parallelization and SIMD vectorization.
    The performance of the matrix-free operator and the geometric multigrid preconditioner is compared to the matrix-based counterparts on the representative numerical example of heterogeneous hyper-elastic material in two and three dimensions.
  \end{abstract}

  \begin{keyword}
      adaptive finite element method \sep
      geometric multigrids \sep
      large strain \sep
      matrix-free \sep
      hyperelasticity
  \end{keyword}

  \end{frontmatter}

@@

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \includegraphics[width=\textwidth]{Emmy_RRZE_timing.eps}
      \caption{vmult}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \includegraphics[width=\textwidth]{Emmy_RRZE_memory.eps}
      \caption{memory consumption}
  \end{subfigure}
  \caption{Heterogeneous 2D large-strain example (Emmy cluster, RRZE).}%
  \label{fig:benchmark_2d_miehe}
\end{figure}

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \includegraphics[width=\textwidth]{IWR_timing.eps}
      \caption{vmult}
  \end{subfigure}
  \begin{subfigure}[b]{0.49\textwidth}
      \centering
      \includegraphics[width=\textwidth]{IWR_memory.eps}
      \caption{memory consumption}
  \end{subfigure}
  \caption{Heterogeneous 2D large-strain example (IWR cluster).}%
  \label{fig:benchmark_2d_miehe_IWR}
\end{figure}
